---
title: "Worksheet 6"
author: "Kylene Joy Yanguas"
date: "2022-11-25"
output: pdf_document
---



#1. How many columns are in mpg dataset? How about the number of rows? Show the
#codes and its result.
```{r, include = TRUE}
library(ggplot2)
library(dplyr)

data(mpg)
as.data.frame(data(mpg))
str(mpg)

nrow(mpg)
ncol(mpg)
```
#The are 234 rows and 11 columns in mpg dataset.

#2. Which manufacturer has the most models in this data set? Which model has the most
#variations? Ans:
```{R, include = TRUE}
manu1 <- mpg %>% group_by(manufacturer) %>%  tally(sort = TRUE)
```
#Dodge Manufacturer has the most models in this data set with 37 models.  
#Toyota Manufacturer has 6 variation namely; 4runner 4wd,camry,camry solara,corolla, 	
#land cruiser wagon 4wd, toyota tacoma 4wd which has the most variation. 

#a. Group the manufacturers and find the unique models. Copy the codes and result.
```{r, include = TRUE}
data <- mpg
data_mpg <- data %>% group_by(manufacturer, model) %>%
         distinct() %>% count()
   data_mpg
colnames(data_mpg) <- c("Manufacturer", "Model","Counts")
   data_mpg
```
#b. Graph the result by using plot() and ggplot(). Write the codes and its result.
```{r, include = TRUE}
qplot(data = mpg, geom = "bar", model, fill=manufacturer)
     
ggplot(mpg, aes(model, manufacturer)) + geom_point()  
```
#3. Same data set will be used. You are going to show the relationship of the model and
#the manufacturer.
```{r, include = TRUE}
data <- mpg

data_mpg1 <- data %>% group_by(manufacturer, model) %>%
  distinct() %>% count()
data_mpg1

colnames(data_mpg1) <- c("Manufacturer", "Model")
data_mpg1
```
#a. What does ggplot(mpg, aes(model, manufacturer)) + geom_point() show?
```{r, include = TRUE}
ggplot(mpg, aes(model, manufacturer)) + geom_point()
```
#It shows the scatter plot of the model and manufacturer of mpg data set. 

#b. For you, is it useful? If not, how could you modify the data to make it more
#informative?
#It is useful, but for somehow the model name below isn't clear enough to modify
#the data clearly and accurately. I preferred to use the bar graph to modify the data to make it more informative. 

#4. Using the pipe (%>%), group the model and get the number of cars per model. Show
#codes and its result.
```{r, include = TRUE}
data <- mpg
data_mpg2 <- data %>% group_by(manufacturer, model) %>%
  distinct() %>% count()
data_mpg2

colnames(data_mpg2) <- c("Model", "Counts")
data_mpg2
```

#a. Plot using the geom_bar() + coord_flip() just like what is shown below. Show
#codes and its result.
```{r, include = TRUE}
qplot(model,
      data = mpg, main = "Number of Cars per Model", 
      xlab = "Model",
      ylab = "Number of Cars", 
      geom = "bar", fill = manufacturer) + coord_flip()
```
#b. Use only the top 20 observations. Show code and results.
```{r, include = TRUE}
head(mpg, n=20)
```
#5. Plot the relationship between cyl - number of cylinders and displ - engine displacement using geom_point with aesthetic colour = engine displacement.
#Title should be “Relationship between No. of Cylinders and Engine Displacement”.
#a. Show the codes and its result.
```{r, include = TRUE}
ggplot(data = mpg , mapping = aes(x = displ, y = cyl, 
                       main = "Relationship between No of Cylinders and Engine Displacement")) + 
geom_point(mapping=aes(colour = "engine displacement")) + geom_jitter()
```
#b. How would you describe its relationship?
#The data shows that the graph is jittered. The color pink indicates as engine displacement which on a straight horizontal position.   

#6. Get the total number of observations for drv - type of drive train (f = front-wheel drive, r = rear wheel drive, 4 = 4wd) and class - type of class (Example: suv, 2 seater, etc.).
#Plot using the geom_tile() where the number of observations for class be used as a fill for aesthetics.

#a. Show the codes and its result for the narrative in #6.
```{r, include = TRUE}
ggplot(data = mpg, mapping = aes(x = drv, y = class)) + 
  geom_point(mapping=aes(color=class)) +
  geom_tile()
```
#b. Interpret the result.
#The data shows that the total number of observations for drv - type of drive train are covered with black
#were mapped using the mapping geometric point graph.

#7. Discuss the difference between these codes. Its outputs for each are shown below.
```{r, include = TRUE}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy, colour = "blue"))

ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy), colour = "blue")
```
#8. Try to run the command ?mpg. What is the result of this command?
```{r, include = TRUE}
?mpg 
```
#This command shows about the mpg dataset. 

 # a. Which variables from mpg data set are categorical?
 #The variable that is categorical are the following:
 #manufacturer, model, year of manufacturer, trans, dtr, cyl, drv, cty, highwat miles per gallon, and fluel type 
 
 # b. Which are continuous variables?
 #The continuous variable is displ(engine displacement, in liters).
 
 #c. Plot the relationship between displ (engine displacement) and hwy(highway miles
 #per gallon). Mapped it with a continuous variable you have identified in 
 #5-b. What is its result? Why it produced such output?
 
 ```{r, include = TRUE}
 
  ggplot(mpg, aes(x = displ, y = hwy, colour = cty)) + geom_point()
  
```
#9. Plot the relationship between displ (engine displacement) and hwy(highway miles
#per gallon) using geom_point(). Add a trend line over the existing plot using
#geom_smooth() with se = FALSE. Default method is “loess”.
```{r, include = TRUE}
  ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) +
  geom_point(mapping=aes(color=class)) +
  geom_smooth(se = FALSE)
```
#10. Using the relationship of displ and hwy, add a trend line over existing plot. Set the
#se = FALSE to remove the confidence interval and method = lm to check for linear modeling.
```{r, include = TRUE}
  ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = class)) +
  geom_point() +
  geom_smooth(se = FALSE)
```
